SSS

### 2019-12-31 NIME_PAPER/SSS.tex
methodology and related work

\begin{abstract}
With the generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds. The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\ 
Following the Unix Philosophy \cite{gancarz2003linux}, we designed our software such that we can utilize our components in various ways leading to different outcomes; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear". Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
\item random generation \item multivariate distribution sampling and \item evolutionary search.\\
\end {enumerate*} 
Finally, we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}. We aim to ameliorate this issue by presenting a copyright free sample-pack of categorized percussion sounds. Furthermore, we have included in our project source code \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} a set of scripts to further expand the sample pack via royalty free sources. 
\keywords{drum, percussion, synthesis, MIR, ML, genetic, search}
\end{abstract}
% See template for CCS classification. 
\ccsdesc[500]{Applied computing~Sound and music computing}
\ccsdesc[500]{Information systems~Music retrieval}
\printccsdesc

\section{Introduction}
The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years. Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly refered to as pads or textures), percussive or melodic loops etc. Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}. Furthermore VST plug-ins can emulate complex audio synthesizers or effects, which some producers may find daunting to work with from scratch. In many cases, VST plug-in vendors or unaffiliated enthusiasts may sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.\\
\section{Implementation}
\subsection{Design}
Towards our goal of generating original audio, we assumed that there are at least 2 major components needed:
\begin{itemize}
    \item A flexible, deterministic, and tractable generator which can create audio
    \item An ear that returns an evaluation of an audio sample; used to determine whether the audio sample fulfills the requirements. 
\end{itemize}

>>>>

\begin{abstract}
With the generation of novel, high quality, one shot percussive sounds as our end goal, we implemented a set of modular software components utilized to form a pipeline for guided generation of sounds. The most crucial of these components are a "virtual ear" capable of evaluating a sounds proximity to different drum types and an efficient, tractable "virtual synthesizer" with a rich set of parameters and DSP methods capable of generating a wide range of sounds.\\ 
Following the Unix Philosophy \cite{gancarz2003linux}, we designed our software such that we can utilize our components in various ways leading to different outcomes; hence, in order to established an adequate level of confidence in our components, we discuss the implementation, limitations, and evaluations of the "virtual synthesizer" and "virtual ear". Next, we present our findings and assessments in regards to the three different methodologies utilized for the generative process of percussive sounds:  \begin {enumerate*} [label=(\roman*)]
\item random generation \item multivariate distribution sampling and \item evolutionary search.\\
\end {enumerate*} 
Additionally, as we observed a general lack of copyright-free percussive sample-packs as well as a lack of unified approach for obtaining such a data-set by fellow researchers \cite{aouameur2019neural,ramires2019timbfeat}, we aim to ameliorate the issue by presenting a copyright free sample-pack of categorized percussion sounds. Furthermore, we have included in our project source code \footnote{\url{https://github.com/imilas/Synths_Stacks_Search}} a set of scripts to further expand the sample pack via royalty free sources. 
\keywords{drum, percussion, synthesis, MIR, ML, genetic, search}
\end{abstract}
% See template for CCS classification. 
\ccsdesc[500]{Applied computing~Sound and music computing}
\ccsdesc[500]{Information systems~Music retrieval}
\printccsdesc

\section{Introduction}
\subsection{Motivation}
The rise of Digital Audio Workstations (DAW) \cite{leider2004digital} and Virtual Studio Technology (VST) based plug-ins \cite{tanev2013virtual} have rapidly transformed the sonic and material landscape of music production in the recent years. Coupled with this rise in popularity is a vast array of commercial products and services dedicated to satiating the need of amateur and professional music producers for unique sounds; most commonly via audio samples: one-shot drum samples, long sustained notes (commonly refered to as pads or textures), percussive or melodic loops etc. Two notable examples of these commercial services are \textit{loopmasters}\footnote{loopmasters.com} and \textit{splice.com}\footnote{splice.com}. Furthermore VST plug-ins can emulate complex audio synthesizers and effects, which some producers may find daunting to work with from scratch. In many cases, VST plug-in vendors or unaffiliated enthusiasts may sell additional presets for these plugins, targeted towards producers who do not have the time or interest in creating their own.\\

\subsection{Methodology and Related Work}
Numerous deep, Neural Network models have been proposed and utilized for the purpose of signal generation in recent years. WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples by \cite{aouameur2019neural,ramires2019timbfeat}. In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it meets several unique requirements:
\begin{enumerate}[label=\roman*]
  \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}. 
  \item Rendering at high sampling rates with little performance issues: A significant number of untrained ears can detect a change in quality between sampling rates of 192 khz and 44.1 khz \cite{reiss2016meta}, with a dramatic increase following extensive training. Thus we can assume that most producers would prefer their audio samples to have as high of a resolution as possible. However, most commonly to speed up performance, the standard sampling rate in most audio generation work neural networks appears to be 24 khz or less \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
  \item Neural networks are often viewed as unexplainable black box solutions. Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset. However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}. The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable. 
\end{enumerate}

\section{Implementation}
\subsection{Design}
Towards our goal of generating original audio, we assumed that there are at least 2 major components needed:
\begin{itemize}
    \item A flexible, deterministic, and tractable generator which can create audio
    \item An ear that returns an evaluation of an audio sample; used to determine whether the audio sample fulfills the requirements. 
\end{itemize}
